---
title: "Developing Data Products - Week 4"
author: "MJL"
date: "February 21, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Introduction
This peer assessed assignment has two parts. First, I created a Shiny application and deploy it on Rstudio's servers. Second, I used Rstudio Presenter to prepare a reproducible pitch presentation about my application.
I selected to predict Miles per Gallon for cars with 4 specific characteristics that you may be interested in;

* Number of Cylinders (4,6,8)
* Gross Horsepower
* Weight (in Tons)
* Transmission type (Automatic, Manual)

This shiny app will predict miles per gallon based on your input of these factors

## Documentation
Here is a summary of the mtcars dataset found in the datasets R package. As you can see, the factors were measured in 32 vehicles (years 1973-1974) tested by Motor Trend. The data looks at design, performance, and fuel consumption. Of the 11 variables I selected the 5 described.

```{r data, echo=FALSE}
library(datasets)
data(mtcars)
str(mtcars[,c(1:2,4,6,9)])
```

## Data Exploration
Summary plot of the mtcars data with each of the selected variables plotted against each other

```{r Summary, echo=FALSE}
plot(mtcars[,c(1:2,4,6,9)])

```

## Links
- shiny app: https://mlouricas.shinyapps.io/DevelopingDataProductsWeek4/
- source code: https://github.com/mlouricas/DataDevelopment_Week4
